---
title: "pset4_steiner"
author: "erika steiner"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

In Lopez-Osorio et al (2017), posted on Canvas, the authors undertake an
exploratory study. They ask what sort of factors relating to incidents
of reported domestic violence (DV), and the parties involved, can
predict DV recidivism, where DV recidivism is defined as one or more
repeat calls to the police within six months. Although they test 66
candidate predictors (by my count), they take no account of multiple
testing. Here you re-analyze their results, employing methods to control
both FWER and FDR.

```{r setup, include = FALSE}
# load packages

library("tidyverse")
library("magrittr")
library("knitr")
library("kableExtra")
library("pdftools")
library("stringr")
# library("fixest")
# library("broom")
# library("did")
# library("plm")
#
# library("stargazer")
# library("ivreg")

# get rid of scientific notation
options(scipen=999)

# don't print code
knitr::opts_chunk$set(echo = FALSE)
```

*1. Extract data from Tables 1 through 4 of the article, constructing a
dataset or dataframe that can be analyzed with a statistical package.*

(Per Ed Discussion Board, extracting data from Tables 1 through 5).

```{r create table 1}
# instructions source: https://crimebythenumbers.com/scrape-table.html

# make pdf text file
pdf_text <- pdf_text(
  # file path
  "lopez_osorio_etal_2017.pdf")

# extract text of table 1 on page 5
lotable1 <- pdf_text[[5]] %>% 
  # split table on line breaks
  str_split(., "\n", simplify = TRUE) %>% 
  # remove white spaces
  trimws()

# isolate rows with relevant data
lotable1 <- lotable1[grep("I-1. P", lotable1):
                       grep("last", lotable1)] %>% 
  # remove rows of over-wrapped indicator text, to be added manually later
  # ie only keep rows with numeric results, as indicated by a decimal and number
  keep( ~ str_detect(.x, "\\.\\d+")) %>% 
  # create columns
  str_split_fixed(., " {2,}", 7) %>% 
  # convert to data frame
  data.frame(.)

# add column names for easy reading/editing
names(lotable1) <- c("Indicators",
                       "RR",
                       "ChiSq",
                       "Present",
                       "Absent",
                       "N/S",
                       "PerValid")

# separate RR coefficient from 95% CI for easier manipulation
lotable1 %<>%
  mutate(CI = str_extract(RR, "\\[[0-9.]+-[0-9.]+\\]\\*{0,3}"),
         RR = str_extract(RR, "^[0-9.]+"),
         # and add column identifying origin table
         OriginTable = 1,
         # fix indicator names for readibility
         # https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
         Indicators = case_when(
           grepl("I-1. P", Indicators) ~ "I-1. Presence of any type of violence carried out by the aggressor",
           grepl("I-5", Indicators) ~ "I-5. Victim's defensive reaction to physical aggression",
           grepl("I-6", Indicators) ~ "I-6. Use of weapons/objects against partner",
           grepl("I-7", Indicators) ~ "I-7. The aggressor has access to firearms",
           grepl("I-8", Indicators) ~ "I-8. The aggressor is an expert in combat techniques",
           grepl("I-9", Indicators) ~ "I-9. Presence of threats/plans aimed to cause the victim harm",
           grepl("Serious threats", Indicators) ~ "Serious threats from the aggressor",
           grepl("Suicide threats", Indicators) ~ "Suicide threats from the aggressor",
           grepl("Economic", Indicators) ~ "Economic threats from the aggressor",
           grepl("Death", Indicators) ~ "Death threats from the aggressor",
           grepl("Threats to child", Indicators) ~ "Threats to children's integrity/custody",
           grepl("I-10.", Indicators) ~ "I-10. An escalation in aggression or threats in the last 6 months",
        .default = as.character(Indicators) )
         ) 
  
# reorder so CI next to RR
lotable1 <-
  lotable1[, c("Indicators",
                 "RR",
                 "CI",
                 "ChiSq",
                 "Present",
                 "Absent",
                 "N/S",
                 "PerValid",
               "OriginTable")]

```

```{r creating table 2}
# extract table 2 on page 6
lotable2 <- pdf_text[[6]] %>% 
  # split table on line breaks
  str_split(., "\n", simplify = TRUE) %>% 
  trimws()

# isolate rows with relevant data
lotable2 <- lotable2[grep("I-11. T", lotable2):
                       grep("violence history", lotable2)] %>% 
  # remove rows of over-wrapped indicator text, to be added manually later
  # ie only keep rows with numeric results, as indicated by a decimal and number
  keep( ~ str_detect(.x, "\\.\\d+")) %>% 
  # create columns
  str_split_fixed(., " {2,}", 7) %>% 
  # convert to data frame
  data.frame(.)

# add column names for easy reading

names(lotable2) <- c("Indicators",
                       "RR",
                       "ChiSq",
                       "Present",
                       "Absent",
                       "N/S",
                       "PerValid")

# separate RR coefficient from 95% CI
lotable2 %<>%
  mutate(CI = str_extract(RR, "\\[[0-9.]+-[0-9.]+\\]\\*{0,3}"),
         RR = str_extract(RR, "^[0-9.]+"),
         # and add column identifying origin table
         OriginTable = 2,
         # fix indicator names for readibility
         # https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
         Indicators = case_when(
           grepl("I-11. T", Indicators) ~ "I-11. They have shown exaggerated jealousy or have suspected their partner of infidelity in the last 6 months",
           grepl("I-12", Indicators) ~ "I-12. They have shown controlling behaviors in the last 6 months",
           grepl("Controlling behaviors towards", Indicators) ~ "Controlling behaviors towards academic/labor aspects",
           grepl("I-13", Indicators) ~ "I-13. In the last 6 months they have shown harassing behaviors",
           grepl("I-14", Indicators) ~ "I-14.In the last year they have done material damage",
           grepl("I-15", Indicators) ~ "I-15. In the last year they have disrespected an authority figure",
           grepl("I-16.", Indicators) ~ "I-16. In the last year they have committed an aggression against third parties and/or animals.",
           grepl("I-17.", Indicators) ~ "I-17. In the last year they have made threats and slights towards third parties.",
           grepl("I-18.", Indicators) ~ "I-18. Presence of problems in their life in
the last 6 months.",
           grepl("I-20.", Indicators) ~ "I-20. Presence of past breakings of sentence conditions",
           grepl("I-21.", Indicators) ~ "I-21. Presence of physical/sexual aggression records",
           grepl("I-22.", Indicators) ~ "I-22. Presence of gender violence records against other partners",
grepl("I-23.", Indicators) ~ "I-23. Presence of mental/psychiatric disorder",
grepl("I-25.", Indicators) ~ "I-25. Presence of any type of addiction or substance abuse (alcohol and drugs)",
grepl("I-26.", Indicators) ~ "I-26. Presence of a gender or domestic violence history within their family",
        .default = as.character(Indicators) )
)
  
# reorder so CI next to RR
lotable2 <-
  lotable2[, c("Indicators",
                 "RR",
                 "CI",
                 "ChiSq",
                 "Present",
                 "Absent",
                 "N/S",
                 "PerValid",
               "OriginTable")]
```

```{r creating table 3}
# extract table 3 on page 7
lotable3 <- pdf_text[[7]] %>% 
  # split table on line breaks
  str_split(., "\n", simplify = TRUE) %>% 
  trimws()

# isolate rows with relevant data
lotable3 <- lotable3[grep("I-27. P", lotable3):
                       grep("care", lotable3)] %>% 
  # remove rows of over-wrapped indicator text, to be added manually later
  # ie only keep rows with numeric results, as indicated by a decimal and number
  keep( ~ str_detect(.x, "\\.\\d+")) %>% 
  # create columns
  str_split_fixed(., " {2,}", 7) %>% 
  # convert to data frame
  data.frame(.)

# add column names for easy reading

names(lotable3) <- c("Indicators",
                       "RR",
                       "ChiSq",
                       "Present",
                       "Absent",
                       "N/S",
                       "PerValid")

# separate RR coefficient from 95% CI
lotable3 %<>%
  mutate(CI = str_extract(RR, "\\[[0-9.]+-[0-9.]+\\]\\*{0,3}"),
         RR = str_extract(RR, "^[0-9.]+"),
         # and add column identifying origin table
         OriginTable = 3,
         # fix indicator names for readibility
         # https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
         Indicators = case_when(
           grepl("I-27.", Indicators) ~ "I-27. Presence of any type of disability",
           grepl("I-28.", Indicators) ~ "I-28. Victim is in gestation period",
           grepl("I-29.", Indicators) ~ "I-29. Victim suffers from a serious illness",
           grepl("I-31.", Indicators) ~ "I-31. Victim has no social/family support",
           grepl("I-32.", Indicators) ~ "I-32. Victim has a mental/psychiatric disorder",
           grepl("I-33.", Indicators) ~ "I-33. Victim has suicidal ideas/attempts",
           grepl("I-34.", Indicators) ~ "I-34. Victim has any kind of addiction or engages in substance abuse (alcohol and drugs)",
           grepl("I-35.", Indicators) ~ "I-35. There is a history of gender or domestic violence within their family",
           grepl("I-36.", Indicators) ~ "I-36. Victim is economically dependent on the aggressor",
           grepl("I-37.", Indicators) ~ "I-37. Victim has minors or family members under their care",
        .default = as.character(Indicators) )
)
  
# reorder so CI next to RR
lotable3 <-
  lotable3[, c("Indicators",
                 "RR",
                 "CI",
                 "ChiSq",
                 "Present",
                 "Absent",
                 "N/S",
                 "PerValid",
               "OriginTable")]
```

```{r creating table 4}
# extract table 4 on page 8
lotable4 <- pdf_text[[8]] %>% 
  # split table on line breaks
  str_split(., "\n", simplify = TRUE) %>% 
  trimws()

# isolate rows with relevant data
lotable4 <- lotable4[grep("I-38", lotable4):
                       grep("or even of killing them", lotable4)] %>% 
  # remove rows of over-wrapped indicator text, to be added manually later
  # ie only keep rows with numeric results, as indicated by a decimal and number
  keep( ~ str_detect(.x, "\\.\\d+")) %>% 
  # create columns
  str_split_fixed(., " {2,}", 7) %>% 
  # convert to data frame
  data.frame(.)

# add column names for easy reading

names(lotable4) <- c("Indicators",
                       "RR",
                       "ChiSq",
                       "Present",
                       "Absent",
                       "N/S",
                       "PerValid")

# separate RR coefficient from 95% CI
lotable4 %<>%
  mutate(CI = str_extract(RR, "\\[[0-9.]+-[0-9.]+\\]\\*{0,3}"),
         RR = str_extract(RR, "^[0-9.]+"),
         # and add column identifying origin table
         OriginTable = 4, 
         # fix indicator names for readibility
         # https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
         Indicators = case_when(
           grepl("I-38.", Indicators) ~ "I-38. The victim has withdrawn complaints in the past",
           grepl("I-39.", Indicators) ~ "I-39. The victim has suffered gender violence by the hands of other aggressors in the past",
           grepl("I-40.", Indicators) ~ "I-40. The victim has expressed their desire to end the relationship to the aggressor at least 6 months ago",
           grepl("I-41.", Indicators) ~ "I-41. There have been reports of mutual violence",
           grepl("I-42.", Indicators) ~ "I-42. The victim fears for the physical integrity of the minors or family members under their care",
           grepl("I-43.", Indicators) ~ "I-43. The victim thinks that the aggressor is capable of attacking them in a violent way or even of killing them",
        .default = as.character(Indicators) )
)
  
# reorder so CI next to RR
lotable4 <-
  lotable4[, c("Indicators",
                 "RR",
                 "CI",
                 "ChiSq",
                 "Present",
                 "Absent",
                 "N/S",
                 "PerValid",
               "OriginTable")]
```

```{r creating table 5}
# extract table 4 on page 8
lotable5 <- pdf_text[[9]] %>% 
  # split table on line breaks
  str_split(., "\n", simplify = TRUE) %>% 
  trimws()

# isolate rows with relevant data
lotable5 <- lotable5[grep("I-1. The", lotable5):
                       grep("The victim feels that the risk level is high", lotable5)] %>% 
  # remove rows of over-wrapped indicator text, to be added manually later
  # ie only keep rows with numeric results, as indicated by a decimal and number
  keep( ~ str_detect(.x, "\\.\\d+")) %>% 
  # create columns
  str_split_fixed(., " {2,}", 7) %>% 
  # convert to data frame
  data.frame(.)

# add column names for easy reading

names(lotable5) <- c("Indicators",
                       "RR",
                       "ChiSq",
                       "Present",
                       "Absent",
                       "N/S",
                       "PerValid")

# separate RR coefficient from 95% CI
lotable5 %<>%
  mutate(CI = str_extract(RR, "\\[[0-9.]+-[0-9.]+\\]\\*{0,3}"),
         RR = str_extract(RR, "^[0-9.]+"),
         # and add column identifying origin table
         OriginTable = 5, 
         # fix indicator names for readibility
         # https://stackoverflow.com/questions/43696227/mutate-with-case-when-and-contains
         Indicators = case_when(
           grepl("I-1. The aggressor has contacted", Indicators) ~ "I-1. The aggressor has contacted the victim through technological means",
           grepl("I-2. The aggressor has contacted", Indicators) ~ "I-2. The aggressor has contacted the victim through third parties",
           grepl("I-3.", Indicators) ~ "I-3. The aggressor has physically gotten closer to the victim",
           grepl("I-4.", Indicators) ~ "I-4. The aggressor is an escaped convict or is in an unknown location",
           grepl("I-5.", Indicators) ~ "I-5. The aggressor has distanced themselves from the victim",
           grepl("I-7.", Indicators) ~ "I-7. The aggressor exteriorizes a respectful attitude toward the law",
           grepl("I-10.", Indicators) ~ "I-10. The aggressor follows the requirements of the charges and of the family separation",
           grepl("I-11.", Indicators) ~ "I-11. The victim has resumed living with the aggressor",
           grepl("I-12.", Indicators) ~ "I-12. The victim doesn't report any episodes to file a complaint about, and/or turns down the offer of protection",
           grepl("I-13.", Indicators) ~ "I-13. The victim engages in activities that threaten their own security",
           grepl("I-14.", Indicators) ~ "I-14. The victim is in a situation of economical dependency",
           grepl("I-15", Indicators) ~ "I-15. The victim has minors or family member under their care",
           grepl("I-16.", Indicators) ~ "I-16. Judicial proceedings to carry out a separation/divorce unwanted by the aggressor",
           grepl("I-17.", Indicators) ~ "I-17. The victim establishes a new sentimental relationship, which is not approved by the aggressor",
           grepl("I-18.", Indicators) ~ "I-18. The aggressor establishes a new sentimental relationship",
           grepl("I-19.", Indicators) ~ "I-19. The aggressor has a stable economic and labor situation",
           grepl("I-20", Indicators) ~ "I-20. The aggressor has favorable family and social support",
           grepl("I-21.", Indicators) ~ "I-21. Presence of a conflict about their responsibilities in the children’s care",
           grepl("I-22.", Indicators) ~ "I-22. The victim feels that the risk level is nonexistent",
        .default = as.character(Indicators) )
)
  
# reorder so CI next to RR
lotable5 <-
  lotable5[, c("Indicators",
                 "RR",
                 "CI",
                 "ChiSq",
                 "Present",
                 "Absent",
                 "N/S",
                 "PerValid",
               "OriginTable")]
```

```{r merge tables 1-5}
# use rbind
df <- rbind(lotable1, lotable2, lotable3, lotable4, lotable5)

df %>% 
  # mutate(OriginTable = 
  #   case_when(
  #     OriginTable == 1 ~ "1. Reported episode indicators associated with recidivism after 6 months included in the VPR-2015 form.",
  #     OriginTable == 2 ~ "2. Indicators related to the aggressor associated with recidivism after 6 months included in the VPR-2015 form.",
  #     OriginTable == 3 ~ "3. Indicators of victim vulnerability associated with recidivism after 6 months included in the de VPR-2015 form.",
  #     OriginTable == 4 ~ "4. Indicators of aggravating circumstances associated with recidivism after 6 months included in the VPR-2015 form.",
  #     OriginTable == 5 ~ "5. Indicators associated with recidivism cases included in the VPER-2015 form."
  #   )
  # ) %>% 
  select(-OriginTable) %>% 
  kable(col.names = c("Indicators", "RR Coefficient", "95% CI", "ChiSquared", "Present", "Absent", "N/S", "Percent Valid"), caption = "VPR and VPER 2015 form coefficients") %>% 
  kable_paper("striped", full_width = F) %>% 
  pack_rows("Table 1. Reported episode indicators associated with recidivism after 6 months included in the VPR-2015 form.", 1, 24) %>% 
  pack_rows("2. Indicators related to the aggressor associated with recidivism after 6 months included in the VPR-2015 form.", 25, 47) %>% 
  pack_rows("3. Indicators of victim vulnerability associated with recidivism after 6 months included in the de VPR-2015 form.", 48, 58) %>% 
  pack_rows("4. Indicators of aggravating circumstances associated with recidivism after 6 months included in the VPR-2015 form.", 59, 64) %>% 
  pack_rows("5. Indicators associated with recidivism cases included in the VPER-2015 form.", 65, 88) %>% 
  footnote(
    general = "** p<0.01,
    *** p <0.001,
    IC of ChiSq is 95%,
    The N/S Cateogry (missing data) groups the cases where this option was marked and the lost cases together."
  )




```

*2. The authors use chi-square statistics to test for association
between their candidate predictors and DV recidivism. On the basis of
the authors’ analysis, how many significant predictors are there at the
5 percent level?*

```{r q2, include = FALSE}
# for chi square, critical value of p < 0.05 is 3.841

# find number of indicators with critical value > 3.841
# for all indicators
df %>% 
  filter(ChiSq > 3.841) %>% 
  nrow()

# results = 29

# for all indicators tables 1-4
df %>% 
  filter(!(OriginTable == 5)) %>% 
  filter(ChiSq > 3.841) %>% 
  nrow()

# results = 16

# for major indicators only
df %>% 
  # only indicators with "I" in indicators name
  filter(grepl("I-", Indicators)) %>% 
  filter(ChiSq > 3.841) %>% 
  nrow()

# results = 22

# for major indicators only
df %>% 
  filter(!(OriginTable == 5)) %>%
  # only indicators with "I" in indicators name
  filter(grepl("I-", Indicators)) %>% 
  filter(ChiSq > 3.841) %>% 
  nrow()

# results = 10
```

For a 2x2 table (Chi-Squared test), there is only 1 degree of freedom.
The corresponding critical Chi-S value for p \< 0.05 is thus 3.841.
"Significant predictors" are thus those with Chi-Squared results greater
than 3.841.

If we look at all indicators, including sub-indicators (those without an
"I-" preceding their name), there are 29 significant predictors across
tables 1-5; 16 of these indicators are from one of the first 4 tables.

If we limit our investigation to only major indicators (those with "I-"
preceding their name), there are 22 significant predictors; 10 of these
significant predictors are from tables 1-4.

```{r}
# TK
# If there is time, make a data table where all of these indicators are highlighted
```

*3. Obtain p-values associated with the chi-square statistics and plot
their distribution. Under the null hypothesis, one can show that
p-values are uniformly distributed. Given that, would you say the
predictors are basically all noise, or does the histogram suggest there
is some predictive signal among them?*

```{r 3 obtain p values}
df %>% 
  mutate(pval =
           )
```

4\. Construct Bonferroni p-values. Controlling the FWER at 5 percent,
which predictors are significant? Which predictors lose their
significance when you account for multiple testing using the Bonferroni
correction?

5\. Now test for significance using the Benjamini-Hochberg approach,
controlling the FDR at 5 percent. Produce a useful visualization that
illustrates how the procedure works. According to this criterion, how
many of the features are significant? In expectation, how many of these
are false discoveries?

6\. Compute the probability that each test represents a false discovery.
This requires solving one equation in one unknown for each test.

7\. Produce a concise listing of the predictors and the various test
results indicating which of them are significant according to the
various testing procedures. Also show which are not significant
according to any test. Do the most- or least-significant predictors
follow any pattern? What about those in between, i.e., those which are
significant according to some procedures but not others?

8\. Considering the objectives of the research study, which do you think
is the more appropriate approach to multiple testing, FWER control or
FDR control? Explain.

9\. It is a complete coincidence that the authors’ unadjusted testing
procedure and the Benjamini-Hochberg procedure produce similar numbers
of significant predictors. Can you explain why this is the case? Hint:
think about the graph you produced in question 5 and the listing you
produced in question 7.

10\. Does accounting for multiple testing lead you to draw different
conclusions than those of Lopez-Osorio et al regarding the factors that
predict DV recidivism? Explain.
